---
title: "Assignment 2 Starter Analysis"
format: html
---

## Setup

```{r}
#| message: false
#| warning: false
library(readr)
library(dplyr)
```

## Load Data

```{r}
# AI-AUDIT: AI helped confirm the repository-root-relative path; verified by rendering from the project root.
nhanes <- read_csv("examples/nhanes-equity/data/nhanes_equity_v6.csv", show_col_types = FALSE)
```

## Inspect

```{r}
cat("Rows:", nrow(nhanes), "\nColumns:", ncol(nhanes), "\n")
names(nhanes)

variable_inspection <- data.frame(
  variable = names(nhanes),
  type = vapply(nhanes, function(column) class(column)[1], character(1)),
  missing = colSums(is.na(nhanes))
)
variable_inspection
```

## Summarize

Compare body mass index (BMI) across income groups, using records with non-missing BMI and income group.

```{r}
 # AI-AUDIT: AI helped shape this analysis-ready pipeline; checked that it excludes missing analysis fields and retains the intended variables.
nhanes_analysis <- nhanes |>
  filter(!is.na(BMI), !is.na(IncomeGroup)) |>
  mutate(IncomeGroup = trimws(IncomeGroup)) |>
  select(IncomeGroup, BMI, Age, Gender)

bmi_summary <- nhanes_analysis |>
  group_by(IncomeGroup) |>
  summarise(
    n = n(),
    mean_bmi = mean(BMI),
    sd_bmi = sd(BMI),
    .groups = "drop"
  )

bmi_summary
```

## Function

```{r}
 # AI-AUDIT: AI helped draft this reusable numeric summary; verified against the complete-case BMI data above.
mean_sd <- function(x) {
  values <- x[!is.na(x)]
  data.frame(
    n = length(values),
    mean = mean(values),
    sd = sd(values)
  )
}

mean_sd(nhanes_analysis$BMI)
```

## Save Output

```{r}
dir.create("output", recursive = TRUE, showWarnings = FALSE)
write_csv(bmi_summary, "output/summary_table.csv")
```

## AI Audit Note

AI assistance was used to organize the requested inspection, analysis-ready pipeline, summary function, and output-writing code. The CSV path and output path were checked by rendering from the repository root. The rendered inspection shows the dataset dimensions, column names, inferred types, and missing-value counts; the analysis excludes rows missing BMI or income group before calculating group summaries. The note was rendered successfully and the saved CSV was checked for its required filename and contents.
